Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

The raw data contains metadata `r nrow(fenraw)` and `r nrow(kunraw)` documents in Fennica and Kungliga, respectively. After initial preprocessing and limiting the analysis between the years `r min(df0$publication_year)`-`r max(df0$publication_year)`, we had `r nrow(subset(df0, catalog == "Fennica"))` and `r nrow(subset(df0, catalog == "Kungliga"))` documents for Fennica and Kungliga, respectively.

>>>>

The raw data contains metadata `r nrow(fenraw)` and `r nrow(kunraw)` documents in Fennica and Kungliga, respectively. We limited the present analysis in the time interval `r min(df0$publication_year)`-`r max(df0$publication_year)`, yielding a subset of `r nrow(subset(df0, catalog == "Fennica"))` (`r round(100*nrow(subset(df0, catalog == "Fennica"))/nrow(fenraw), 1)`%) and `r nrow(subset(df0, catalog == "Kungliga"))` (`r round(100*nrow(subset(df0, catalog == "Kunliga"))/nrow(kunraw), 1)`%) documents for Fennica and Kungliga, respectively.
